Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-08 paper/background.tex
Paper update

The objective function $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} can be approximated by Gaussian
process (GP) model~\cite{GPML}. The GP model is the most commonly used model
for Bayesian optimization. The advantage of GP is that it provides a
well-calibrated uncertainty of prediction. GP is characterized by a mean
function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In this
work, we use squared-exponential ARD kernel, and a constant mean function
$m(\bm{x}) = \mu_0$ for all our experiments.

Given a new data point $\bm{x}$, the prediction of $f(\bm{x})$ is
not a scalar value, but a predictive distribution
\begin{equation}
f(\bm{x}) \sim N(\mu(\bm{x}),
\sigma^2(\bm{x})),
\label{eq:GPRPred}
\end{equation}
where $\mu(\bm{x})$ and $\sigma^2(\bm{x})$ can be expressed as
\begin{equation}
        \begin{array}{lll}
            \mu(\bm{x})      &=& \mu_0 + k(\bm{x},X)K^{-1}(\bm{y} - \mu_0) \\
            \sigma^2(\bm{x}) &=& k(\bm{x}, \bm{x}) - k(\bm{x}, X)K^{-1}k(X, \bm{x}),
        \end{array}
    \label{eq:GPRPredEqNoisy}
\end{equation}
where $k(\bm{x}, X) = (k(\bm{x}, \bm{x}_1), \dots, k(\bm{x},
\bm{x}_N))^T$ and $k(X, \bm{x}) = k(\bm{x}, X)^T$. The
$\mu(\bm{x})$ can be viewed as the prediction of the function value, while
the $\sigma^2(\bm{x})$ is a measure of uncertainty of the prediction. The hyperparameters including the parameters of the kernel function, and $\mu_0$ can be obtained by Maximum Likelihood Estimation (MLE) based on the training data set.

>>>>

The objective function $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} can be
approximated by Gaussian process (GP) model~\cite{GPML}. The GP model is the
most commonly used model for Bayesian optimization. The advantage of GP is that
it provides a well-calibrated uncertainty of prediction. GP is characterized by
a mean function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In
this work, we use squared-exponential ARD kernel, and a constant mean function
$m(\bm{x}) = \mu_0$ for all our experiments, by default, we assume the
objective function evaluations are noisy and let GP to infer the noise level
$\sigma_n$, the introduction of the $\sigma_n$ level also helps to improve the
numerical stability.

Given a new data point $\bm{x}$, the prediction of $f(\bm{x})$ is
not a scalar value, but a predictive distribution
\begin{equation}
f(\bm{x}) \sim N(\mu(\bm{x}),
\sigma^2(\bm{x})),
\label{eq:GPRPred}
\end{equation}
where $\mu(\bm{x})$ and $\sigma^2(\bm{x})$ can be expressed as
\begin{equation}
        \begin{array}{lll}
            \mu(\bm{x})      &=& \mu_0 + k(\bm{x},X)[K+\sigma_n^2I]^{-1}(\bm{y} - \mu_0) \\
            \sigma^2(\bm{x}) &=& k(\bm{x}, \bm{x}) - k(\bm{x}, X)[K+\sigma_n^2]^{-1}k(X, \bm{x}),
        \end{array}
    \label{eq:GPRPredEqNoisy}
\end{equation}
where $k(\bm{x}, X) = (k(\bm{x}, \bm{x}_1), \dots, k(\bm{x},
\bm{x}_N))^T$ and $k(X, \bm{x}) = k(\bm{x}, X)^T$. The
$\mu(\bm{x})$ can be viewed as the prediction of the function value, while
the $\sigma^2(\bm{x})$ is a measure of uncertainty of the prediction.

### 2018-02-08 paper/experiments.tex
Paper update

The proposed MACE algorithm was tested using eight benchmark functions and two
real-world circuits. Four state-of-the-art parallel Bayesian optimization
methods were compared, including the BLCB algorithm, the local penalization
method with EI acquisition function, the qEI and qKG methods\footnote{We
implemented the BLCB algorithm as the available open source implementations only
allow discrete input. For the EI-LP method, the code is downloaded from
https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is
downloaded from https://github.com/wujian16/Cornell-MOE}.

@@

For all functions except the two 10D functions, we set the number of initial
random sampling to $N_{init} = 20$ and the number of iterations to $N_{iter} =
45$. Batch size is set to $B = 4$, the total number of function evaluations is
$N_{init} + B \times N_{iter}$. For the 10D Ackley and 10D Rosenbrock functions, we
$N_{init} = 100$ and $N_{iter} = 175$. The experiments were repeated ten
times to average the random fluctuations.

>>>>

The proposed MACE algorithm was tested using eight benchmark functions and two
real-world circuits. For the two test circuits, we used HSPICE 2012.06 to as
the simulator to get circuit performances.

Four state-of-the-art parallel Bayesian optimization methods were compared,
including the BLCB algorithm, the local penalization method with EI acquisition
function, the qEI and qKG methods\footnote{We implemented the BLCB algorithm as
the available open source implementations only allow discrete input. For the
EI-LP method, the code is downloaded from
https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is downloaded
from https://github.com/wujian16/Cornell-MOE}. For the MACE, BLCB, and EI-LP
method, the ARD squared-exponential kernel is used and the GP models are fitted
by maximum likelihood estimations(MLE); for the qKG and qEI methods, the
Matern52 kernel is used, and the GP hyperparameters are integrated via MCMC
sampling. The Matern52 kernel and MCMC integration are the default strategies
of the qKG and qEI implementations and it is unclear in the documentation about
how to change the GP settings.

@@

For all functions except the two 10D functions, we set the number of initial
random sampling to $N_{init} = 20$ and the number of iterations to $N_{iter} =
45$. Batch size is set to $B = 4$, the total number of function evaluations is
$N_{init} + B \times N_{iter}$. For the 10D Ackley and 10D Rosenbrock functions, we set
$N_{init} = 100$ and $N_{iter} = 175$. The experiments were repeated ten
times to average the random fluctuations.
